An accelerated algorithm for finding efficient solutions in multiobjective problems with black-box multiextremal criteria\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2022-06-30 2022/OPTIMA/paper.tex
reduce number of references, 16 pages now

Note that special classes of multiextremal optimization problems arise when the criteria can be described analytically. In this case one can apply efficient methods based on d.c. optimization approach \cite{Strekalovsky2001,Strekalovsky2003,Strekalovsky2020}. However, this paper considers a completely different case, when the analytical expressions for the functions are not known. This situation is typical for finding the best decisions in applied problems in which the evaluation of criteria requires numerical simulation.

@@

As the directions of further development of the current research it would be interesting to investigate the possibilities of applying other schemes of dimensionality reduction, for example,
the nested optimization scheme \cite{Grishagin2016,Grishagin2018}, the diagonal \cite{Sergeyev2015,Sergeyev2017} or simplicial \cite{Zilinskas2011,PaulaviciusZilinskas2014} partition methods
in the framework of the general approach used in the paper. Moreover, the prospective way is to develop parallel versions of the proposed general scheme oriented at powerful supercomputer systems.

>>>>

%Note that special classes of multiextremal optimization problems arise when the criteria can be described analytically. In this case one can apply efficient methods based on d.c. optimization approach \cite{Strekalovsky2001,Strekalovsky2003,Strekalovsky2020}. However, this paper considers a completely different case, when the analytical expressions for the functions are not known. This situation is typical for finding the best decisions in applied problems in which the evaluation of criteria requires numerical simulation.

@@

As the directions of further development of the current research it would be interesting to investigate the possibilities of applying other schemes of dimensionality reduction, for example,
the nested optimization scheme \cite{Grishagin2016,Grishagin2018}, the diagonal \cite{Sergeyev2017} or simplicial \cite{PaulaviciusZilinskas2014} partition methods
in the framework of the general approach used in the paper. Moreover, the prospective way is to develop parallel versions of the proposed general scheme oriented at powerful supercomputer systems.
